Towards a Complete Model of Mutation Selection Balance in Humans

### 2023-01-14 manuscript/manuscript.tex
methods stuff
more ms updates
ms intro

\title{}

@@

\section*{Introduction}
\section*{Results}

>>>>

\title{Towards a Complete Model of Mutation Selection Balance in Humans}

@@

\section*{Introduction}

Eukaryotes genomes are under continual selectionary pressure to remove the
continual influx of deleterious mutations at conserved regions. This purifying
selection process keeps mutations that reduce fitness at low frequency in the
population, and reduces genetic diversity at sites linked to genomic regions
that are predominantly under purifying selection such as coding sequences and
regions that have been shown to be phylogenetically conserved between species.
Evolutionary geneticists have developed a series of mathematical models of this
process, to predict quantities such as the equilibrium level of segregating
deleterious mutations (\emph{genetic load}), and the reduction in neutral
genetic diversity at linked sites due to a faster rate of coalescence (the $B$
reduction factor). Statistical models of the purifying selection process fit to
human genomic data closely match observed patterns of genetic variability along
the genome, explaining around 60\% of the genetic variability at the megabase
scale \parencite{McVicker2009-ax,Murphy2022-sj}.

These evolutionary genetics models only consider the impact of new mutations
that are sufficiently deleterious that they are guaranteed to be eliminated
eventually by selection. When mutations are strongly deleterious, the impact of
random genetic drift and random perturbations caused by selection at linked
neighboring sites (genetic draft) on these mutations on their fates can be
ignored. Under these conditions, mathematical models can assume an stationary
balance between the input of new mutations entering the population at rate
$\mu$ per basepair, per generation, and their rate of loss determined by the
relative reduction in heterozygous fitness, $1-s$. Under these
mutation-selection balance models, the equilibrium genetic load and the
reduction in coalescent time are approximately determined by the ratio
$\nicefrac{\mu}{s}$. However, estimates of the distribution of fitness effects
suggest many new mutations are weakly deleterious, such that their dynamics can
no longer ignore the influence of genetic drift and draft.

To understand the this process and make predictions about the equilibrium level
of deleterious mutations segregating in the population, evolutionary
geneticists have used models of mutation-selection balance. These models

Non-equilibrium models of deleterious mutation flux.

Generalized background selection

These models

\section*{Results}
